\section*{Conclusion}
\paragraph{}
In this project, we explored the IMDB dataset that contains information of a number of movies and their ratings/genres, actor/actress, directors. We constructed an actor network that is connected by costarring movies and explored the relationship between their pagerank score and their actual popularity (which is determined by the opinions from the author). 
\paragraph{}
Aside from that, we also constructed a movie network that is connected by actor/actress starring in multiple movies. From this network we explored its community structure, and relationship between community partitioning and movie genre tagging. We also targeted 3 particular movies : Batman v Superman: Dawn of Justice(2016), Mission: Impossible Rogue Nation(2015) and Minions(2015). We studied the neighbors of these 3 movies and provide a fitting function that predict their ratings based on ratings of their neighbors. However, this just fits a function to 3 samples, which may suffer from overfitting and therefore we moved on to prediction of ratings based on the entirety of dataset.
\paragraph{}
In the last part, we constructed 4 different regression models based on information provided, i.e., page rank score, popularity of the directors, and attempted  to predict the ratings of all movies in the dataset. This turned out to be, to some extend, undesirable as the dimension of the information is not high enough to generate a good fit. Alternatively, we used a bipartite graph to predict ratings, performance of which turned out to be comparable, but not significantly better than regression models. To find out the best number of movies used in computing actor scores and best number of actors used to predict movie ratings, we performed a pipeline analysis and ran through all combinations. With little surprise, the more actors/movies are included, the better the fit. This can be attributed to the fact that, in general fitting problems the more amount of information/data involved, the better the fit.
\paragraph{}
For future reference, we tend to focus on 2 main factors. First, we would like to increase number of tags on each movies and see if this results in a more informative community tagging. Second, we would like to perform further cleansing on movie rating files, as some movies are only rated by few and may serve as outliers. For instance, we observed in ratings files, there exists a number of movies with a rating of 9.9 that are directed and starred by a number of nobodies. As such, we would like to find a method that filters out these outliers and perform analysis on top of it.